COG-ED Manuscript

### 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
looked furher into AUCs

**something is wrong with the AUC calculation**

@@

require(gtools)
demo_data = data.frame(level = rep(1:4,24))
sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
m = 1
for (n in 1:(nrow(demo_data)/4)) {
  demo_data$subject[m:(m+3)] = rep(n,4)
  demo_data$sv[m:(m+3)] = sv[n,]
  m = m + 4
}
subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double())
for (i in 1:(length(subjectindex)-1)) {
  sv_sorted <- sort(demo_data$sv[subjectindex[i]:(subjectindex[i]+3)])
  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
                        auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                   method = "trapezoid"),
                        auc_sv_unsorted = (0.5 * (demo_data$sv[subjectindex[i]] + demo_data$sv[subjectindex[i]+1]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+1] + demo_data$sv[subjectindex[i]+2]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])),
                        auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[2] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[3] + sv_sorted[4])))
  demo_sv <- rbind(demo_sv, newdata)
}
ggplot(demo_data, aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1)

>>>>

@@

require(gtools)
demo_data = data.frame(level = rep(1:4,24))
sv = permutations(n = 4, r = 4, v = c(0.1,0.4,0.85,1))
m = 1
for (n in 1:(nrow(demo_data)/4)) {
  demo_data$subject[m:(m+3)] = rep(n,4)
  #demo_data$sv[m:(m+3)] = sv[n,]
  demo_data$sv[m:(m+3)] = sample(x = c(0.11,0.38,0.45,0.53,0.70,0.85,0.90,1.00), size = 4, replace = FALSE, prob = c(0.025,0.025,0.05,0.05,0.05,0.05,0.05,0.7))
  m = m + 4
}
subjectindex <- c(1,which(demo_data$subject != dplyr::lag(demo_data$subject)),nrow(demo_data))
demo_sv <- data.frame(subject = character(), auc_sv = double(), auc_sv_unsorted = double(),
                      ascent_mean = double(), ascent_sum = double(), auc_x_ascentmean = double())
for (i in 1:(length(subjectindex)-1)) {
  sv_sorted <- sort(demo_data$sv[subjectindex[i]:(subjectindex[i]+3)])
  newdata <- data.frame(subject = demo_data$subject[subjectindex[i]],
                        auc_sv = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                   method = "trapezoid"),
                        auc_sv_unsorted = (0.5 * (demo_data$sv[subjectindex[i]] + demo_data$sv[subjectindex[i]+1]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+1] + demo_data$sv[subjectindex[i]+2]) +
                                               0.5 * (demo_data$sv[subjectindex[i]+2] + demo_data$sv[subjectindex[i]+3])),
                        auc_sv_sorted = (0.5 * (sv_sorted[1] + sv_sorted[2]) +
                                           0.5 * (sv_sorted[2] + sv_sorted[3]) +
                                           0.5 * (sv_sorted[3] + sv_sorted[4])),
                        ascent_mean = ((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3,
                        ascent_sum = (demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]),
                        auc_x_ascentmean = auc(demo_data$level[subjectindex[i]:(subjectindex[i]+3)], demo_data$sv[subjectindex[i]:(subjectindex[i]+3)],
                                               method = "trapezoid") * (((demo_data$sv[subjectindex[i]+3] - demo_data$sv[subjectindex[i]+2]) +
                                        (demo_data$sv[subjectindex[i]+2] - demo_data$sv[subjectindex[i]+1]) +
                                        (demo_data$sv[subjectindex[i]+1] - demo_data$sv[subjectindex[i]]))/3))
  demo_sv <- rbind(demo_sv, newdata)
}
ggplot(demo_data, aes(x=level, y=sv, group=subject)) +
  geom_line(aes(color=subject), size = 1)
